A Method for the Spectroscopic Inference of Stellar Parameters

### 2014-07-28 tex/paper.tex
updated PHOENIX file

% Data description of Gl 51
The spectrum of Gl~51 was obtained with the \emph{SPEX} instrument \citep{rayner03} on the IRTF. The spectrum is a moderate resolution (R $\sim$ 2,000), mid-infrared spectrum from 0.7--5.5$\mu$m at signal to noise $\gt 200$. Gl~51 is a M5 star from the IRTF spectral library \citep{cushing05, rayner09}.

% What other people get when they fit this star. How does our inference compare?
To determine the stellar parameters of Gl~51, \citep{rojas-ayala12} use the 2.205$\mu$m \ion{Na}{1} doublet and 2.263$\mu$m \ion{Ca}{1} triplet and their \HK\ index, defined using three passbands: 2.070--2.090$\mu$m, 2.235--2.255$\mu$m, and 2.360--2.380$\mu$m. The index is designed to probe the curvature of the spectrum pseudo-continuum, which varies to due absorption from water. For a useful visualization of which spectral features these indices track, see their figure 2. The \HK\ index is a monotonic function of temperature, showing more curvature in the spectrum towards cooler $T_{\rm eff}$ and the index is independent of $\Z$ in the range $3000\,{\rm K} \leq T_{\rm eff} \leq 4000\,{\rm K}$. Below $3000~{\rm K}$, the index may appear to be metallicity dependent, although they caution that this may be a computational artifact. They find that the \HK\ index has a negligible dependence on $\log g$. They find that the index correlates with spectral type. \citet{rojas-ayala12} use a custom grid of PHOENIX BT-Settl models run from the PHOENIX web simulator at. The note that the models fit the spectrum match the overall spectral shape well, although the models consistently underpredict the strength of the \ion{Na}{1} and \ion{Ca}{1} lines, even when using the highest metallicity models. \citet{rajpurohit10} note that the oscillator strengths and opacities of the \ion{Na}{1} and \ion{Ca}{1} lines may be incorrect. In the range of stellar parameters for M dwarfs, \citet{rojas-ayala12} note that the strength of the \ion{Na}{1} doublet increases as $T_{\rm eff}$ decreases. The strength of the \ion{Ca}{1} triplet increases as $T_{\rm eff}$ and $\Z$ increase. \todo{What does our analysis yield?} Because the PHOENIX grid by \citet{husser13} has more range/uniformity of parameters, we use this to fit Gl 51.

>>>>

% Data description of Gl 51
The spectrum of Gl~51 was obtained with the \emph{SPEX} instrument \citep{rayner03} on the IRTF. The spectrum is a moderate resolution (R $\sim$ 2,000), mid-infrared spectrum from 0.7--5.5$\mu$m at signal to noise $> 200$. Gl~51 is a M5 star from the IRTF spectral library \citep{cushing05, rayner09}.

% What other people get when they fit this star. How does our inference compare?
To determine the stellar parameters of Gl~51, \citep{rojas-ayala12} use the 2.205$\mu$m \ion{Na}{1} doublet and 2.263$\mu$m \ion{Ca}{1} triplet and their \HK\ index, defined using three passbands: 2.070--2.090$\mu$m, 2.235--2.255$\mu$m, and 2.360--2.380$\mu$m (see their Figure 2 for a useful visualization). The index is designed to probe the curvature of the spectrum pseudo-continuum, which varies to due absorption from water molecules. \citet{rojas-ayala12} use a custom grid of PHOENIX BT-Settl models run from the PHOENIX web simulator at. The note that the models fit the spectrum match the overall spectral shape well, although the models consistently underpredict the strength of the \ion{Na}{1} and \ion{Ca}{1} lines, even when using the highest metallicity models. \citet{rajpurohit10} note that the oscillator strengths and opacities of the \ion{Na}{1} and \ion{Ca}{1} lines may be incorrect. When restricting the spectrum to the range of the indices that they use, we find that \todo{What does our analysis yield? It should be in the table.} Because the PHOENIX grid by \citet{husser13} has more range/uniformity of parameters, we use this to fit Gl 51.
